---
title: "Medium_Test"
author: "Ao Ni"
date: "2019/3/14"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Hello everyone, this is Ao Ni, a senior student major in Statistics who will pursue a master degree in Computer science in the near future.Here is my solution for the medium tests.


```{r, message = FALSE, warning=FALSE}
library(iregnet)
library(glmnet)
library(lasso2)
library(ggplot2)
library(penaltyLearning)
library(rmarkdown)
library(microbenchmark)
data("Prostate")
data('neuroblastomaProcessed')
```

### Run iregnet on neuroblastomaProcessed data

```{r}
X <- neuroblastomaProcessed$feature.mat
Y <- neuroblastomaProcessed$target.mat
Y[abs(Y) == Inf] = NA
summary(X)
```


We can see that some variables have zero variance. Delete them!


```{r}
select.col <- apply(X,2,function(x){
  return(max(x)-min(x)!=0)
})
X = X[,select.col]
set.seed(1)
#fit the data!
fit.ire <- iregnet(x = X, y = Y)
plot(1,1)
#plot(fit.ire)
```
Seems one of the variables has very small variance. I omit it in the next plot.

```{r}
fit.ire$beta <- fit.ire$beta[-c(which.min(fit.ire$beta[,100])),]
#plot(fit.ire)
plot(1,1)
```
